% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage{wasysym}
\usepackage{ marvosym }
\usepackage{csquotes}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Carlos Yero}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:

\address{{\bf Work Address} \\  12006 Rattley Road  \\ Newport News, VA 23606\\
        (786) 387-8667}


\begin{resume}
 
%\section{OBJECTIVE}  
%     A post-doctoral position in the field of Experimental Nuclear Physics 
%     with emphasis on NIM (Nuclear Instrumentation Modules) and CAMAC (Computer
%     Automated Measurement and Control) data-acquisition system. 
 
\section{\footnotesize EDUCATION} Ph.D, Physics Expected: December, 2019  \\
                                  Florida International University, Miami, FL \\ 
                                  Research Topic:\hspace{1mm}\enquote{Deuteron Electro-Disintegration at Very High Missing Momenta} \\
                                  Major Advisor: Dr. Werner Boeglin 


 Magna CUM Laude B.S., Physics (2014)  \\

    
                %GPA: 3.81/4.0 \\


 \section{\footnotesize RESEARCH\\EXPERIENCE}      {\bf Florida International University, Miami, FL} 
 
                 \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Graduate Research} &   August 2014 - present 
                \end{ncolumn}
                \vspace{1mm}
                \begin{itemize}
                
               \item  Currently working on hardware as part of Hall C 12 GeV Upgrade. Specifically, on setting up electronics for various detectors in the High Momentum Spectrometer (HMS) arm. 
              Future plans on setting up a coincidence trigger between the two spectrometer arms, HMS and Super HMS.    
              
              \item  Analyzed strangeness photoproduction data for Jefferson Lab, Hall B g12 Experiment. The analysis focused on extraction of
              polarization observables from $\gamma$p $\rightarrow$ K$^{*}$$\Lambda$ reaction.
                

  \end{itemize}
               
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Undergraduate Research}     &      January 2013 - April 2014 
                \vspace{5mm}
                \end{ncolumn}\begin{itemize}
\item Polished and tested scintillator bars for Jefferson Lab, Hall D Start Counter 
 \end{itemize}
 
 \section{\footnotesize TEACHING\\EXPERIENCE} {\bf Florida International University, Miami, FL} 
 
         \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Recitations} &   August 2015 - April 2016 
                \end{ncolumn}
                \vspace{1mm}
                
                \begin{itemize}
               
                \item  Two semesters of Physics I and II teaching assistant, which focused on problem-solving techniques that 
                      complement the lectures.
                
                \end{itemize}
                
                 \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Introductory Physics Labs} &   August 2015 - April 2016 
                \end{ncolumn}
                \vspace{1mm}
                
                  \begin{itemize}
              
                  \item Two semesters of teaching Physics I and II Laboratory, 
                        in which students develop and strengthen physics 
                        concepts imparted in lectures as well as critical thinking skills.    
                  
                  \end{itemize}
              
              
             
              
 \section{\footnotesize PRESENTATIONS}
\textit{\enquote{Deuteron Electro-Disintegration at Very High Missing Momenta}}, Hampton University
		Graduate Studies (HUGS) Program, NewportNews, VA, June 2016. 
		

\section{\footnotesize SKILLS} Operating Systems: Microsoft Windows Vista/7 and UNIX-Linux \\  
                  Programming Languages: Python and C++  \\
                  Bilingual on English and Spanish




\newpage
\section{REFERENCES}              Dr. Werner U. Boeglin (Major Advisor) \\
                                  Department of Physics \\
                                  Florida International University \\
                                  Miami, FL 33125 \\
                                 \Email \hspace{0.5mm} \href{mailto:boeglinw@fiu.edu}{boeglinw@fiu.edu} \\                           
                                 \phone \hspace{0.5mm} (305) 348-1711 
                                  
                                  Dr. Joerg Reinhold (Professor) \\
                                  Department of Physics \\
                                  Florida International University \\
                                  Miami, FL 33125 \\
                                 \Email \hspace{0.5mm} \href{mailto:reinhold@fiu.edu}{reinhold@fiu.edu} \\                           
                                 \phone \hspace{0.5mm} (305) 348-6422
   
                                  Dr. Mark Jones (JLab Staff Scientist) \\
                                  CEBAF Center - Hall C \\
                                  Thomas Jefferson National Laboratory \\
                                  Newport News, VA 23606 \\
                                 \Email \hspace{0.5mm} \href{mailto:jones@jlab.org}{jones@jlab.org} \\                           
                                 \phone \hspace{0.5mm} (757) 269-7733                               
\end{resume} 
\end{document}





